Historical Soil Organic Carbon Budget

### 2020-01-21 SOCbudgetPaper/discussion.Rmd
Initial commit, 1st draft

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package, which can be downloaded from the different journal webpages.
%% For further assistance please contact Copernicus Publications at: production@copernicus.org
%% https://publications.copernicus.org/for_authors/manuscript_preparation.html

%% copernicus_rticles_template (flag for rticles template detection - do not remove!)

%% Please use the following documentclass and journal abbreviations for discussion papers and final revised papers.

%% 2-column papers and discussion papers
\documentclass[gc, manuscript]{copernicus}

%% Journal abbreviations (please use the same for discussion papers and final revised papers)

% Advances in Geosciences (adgeo)
% Advances in Radio Science (ars)
% Advances in Science and Research (asr)
% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
% Annales Geophysicae (angeo)
% Archives Animal Breeding (aab)
% ASTRA Proceedings (ap)
% Atmospheric Chemistry and Physics (acp)
% Atmospheric Measurement Techniques (amt)
% Biogeosciences (bg)
% Climate of the Past (cp)
% DEUQUA Special Publications (deuquasp)
% Drinking Water Engineering and Science (dwes)
% Earth Surface Dynamics (esurf)
% Earth System Dynamics (esd)
% Earth System Science Data (essd)
% E&G Quaternary Science Journal (egqsj)
% Fossil Record (fr)
% Geochronology (gchron)
% Geographica Helvetica (gh)
% Geoscience Communication (gc)
% Geoscientific Instrumentation, Methods and Data Systems (gi)
% Geoscientific Model Development (gmd)
% History of Geo- and Space Sciences (hgss)
% Hydrology and Earth System Sciences (hess)
% Journal of Micropalaeontology (jm)
% Journal of Sensors and Sensor Systems (jsss)
% Mechanical Sciences (ms)
% Natural Hazards and Earth System Sciences (nhess)
% Nonlinear Processes in Geophysics (npg)
% Ocean Science (os)
% Primate Biology (pb)
% Proceedings of the International Association of Hydrological Sciences (piahs)
% Scientific Drilling (sd)
% SOIL (soil)
% Solid Earth (se)
% The Cryosphere (tc)
% Web Ecology (we)
% Wind Energy Science (wes)

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}

% The "Technical instructions for LaTex" by Copernicus require _not_ to insert any additional packages.
%
\usepackage{algorithmic}
\usepackage{algorithm}

\begin{document}

\title{Historical Soil Organic Carbon Budget}

\Author[1]{Kristine}{Karstens}
\Author[1]{Benjamin Leon}{Bodirsky}
\Author[1]{Alexander}{Popp}

\affil[1]{Potsdam-Institut of Climate Impacts Research, Potsdam, Germany}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

\runningtitle{R Markdown Template for Copernicus}

\runningauthor{Nüst et al.}

\correspondence{Kristine\ Karstens\ (kristine.karstenst@pik-potsdam.de)}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.

\firstpage{1}

\maketitle

\begin{abstract}
SOC one of larges c sinks on earth (3 times larger biospehre pool).
Agricultural management leads to a depletion of soil organic crabon.
However this depletion of soil organic carbon (SOC) pools are so far not
well represented in global assessments of historic carbon emissions.
While SOC models often represent well the biochemical processes that
lead to the accumulation and decay of SOC, the management decisions
driving these biophysical processes are still little investigated. Here
we create a spatial explicit data set for crop residue and manure
management on cropland based on global historic production (FAOSTAT) and
land-use (LUH2) data and combine it with the IPCC Tier 2 approach to
create a half-degree resolution soil organic carbon budget on mineral
soils. We estimate that due to arable farming soils have lost over (?)
GtOC of which (??) GtOC have been released within the period 1990-2010.
Tier 2 IPCC methodolgy estimates higher soil organic carbon losses than
Tier 1 methods, which may origin from \ldots{} . We also find that SOC
is very sensity to management decision such as residue recycling
indicating the nessessity to incorporated better management data in soil
models.
\end{abstract}

\copyrightstatement{The author's copyright for this publication is transferred to
institution/company.}

\introduction

Introduction text goes here. You can change the name of the section if
neccessary using
\texttt{\textbackslash{}introduction{[}modified\ heading{]}}.

The following settings can or must be configured in the header of this
file and are bespoke for Copernicus manuscripts:

\begin{itemize}
\item
  The \texttt{journal} you are submitting to using the official
  abbreviation.
\item
  You can use the function
  \texttt{rticles::copernicus\_journal\_abbreviations(name\ =\ \textquotesingle{}...\textquotesingle{})}
  to search the existing journals.
\end{itemize}

\section{Method (50)}

\subsection{Carbon Budget (50)}

Based on the IPCC guidelines \citep[\citet{IPCC2019}]{IPCC2006} for soil
organic carbon stocks, we combining approaches to estimate SOC stocks by
weighting inflows via dead plant material (see @ref(sec:carboninputs))
against outflows through SOC decay (see @ref(sec:tier1),
@ref(sec:tier2)). Carbon displacement via leaching and erosion is
neglected for this budget.

Connecting carbon inputs with soil carbon dynamics will create a budget
of in- and outflows.

\subsubsection{Soil Carbon turnover following (new) Tier 2 method
(300)}\label{sec:tier2}

Yearly turnover between three different SOC pools for the topsoil is
model using global parameters.

\subsubsection{Soil Carbon turnover following Tier 1
(150)}\label{sec:tier1}

Stock changes are calculated using simple change factors on the SOC
pools for the topsoil.

\subsubsection{Carbon Inputs to the Soil}\label{sec:carboninputs}

Carbon inputs are estimated based on the land use. Whereas cropland
inputs are mainly formed by residue, dead below ground and cover crop
biomass alterate by the corresponding management practice, pasture and
natural vegetation inputs are estimate via modelled annual litterfall
rates. For the former we use various data sets and rule based
approaches, which are specified in @ref(sec:agrimanagement)

\subsection{Agricultural management (50)}\label{sec:agrimanagement}

We combine data sets to estimate agricultural flows and management
decisions on cropland.

\subsubsection{Landuse and Landuse Change (150)}

We use LUH2v2 data for major Landuse types and their transition and fit
cropspecific areas to country scale FAO data.

\subsubsection{Crop Production and Residues (300)}

FAO Production values are combined with Feed estimations from
{[}Isabelles Paper{]} and rule based demand shares. LPJmL yield and LUH
landuse patterns are used to scale down to half-degree.

\subsubsection{Livestock Distribution and Manure Excretion (300)}

Based on {[}Gridded Livestock of the world{]} we use rule based
asumption to estimate livestock and manure distribution on the globe.
Animal waste system shares are used as is {[}Bodirsky{]}.

\subsubsection{Irrigation (100)}

Simple growing period calculations together with irrigation shares of
LUH2v2 are use to estimate water effects on decay rates.

\subsubsection{Tillage (100)}

Tillage data sets of {[}Vera, others{]} together with rules are used to
drive tillage effect on decay rates.

\section{Content section with citations}

See the
\href{http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html}{R
Markdown docs for bibliographies and citations}.

Copernicus supports biblatex and a sample bibliography is in file
\texttt{sample.bib}. Read {[}{]}, and {[}see {]}.

\section{Content section with R code chunks}

You should always use \texttt{echo\ =\ FALSE} on R Markdown code blocks
as they add formatting and styling not desired by Copernicus. The hidden
workflow results in 42.

You can add verbatim code snippets without extra styles by using
\texttt{\textasciigrave{}\textasciigrave{}\textasciigrave{}} without
additional instructions.

\begin{verbatim}
sum <- 1 + 41
\end{verbatim}

\section{Content section with list}

If you want to insert a list, you must

\begin{itemize}
\item
  leave
\item
  empty lines
\item
  between each list item
\end{itemize}

\section{Examples from the official template}

\subsection{FIGURES}

@@

\subsection{FIGURES}

@@

\subsubsection{ONE-COLUMN FIGURES}

Include a 12cm width figure of Nikolaus Copernicus from
\href{https://en.wikipedia.org/wiki/File:Nikolaus_Kopernikus.jpg}{Wikipedia}
with caption using R Markdown.

\subsubsection{TWO-COLUMN FIGURES}

@@

\subsection{TABLES}

@@

\subsubsection{ONE-COLUMN TABLE}

@@

\subsubsection{TWO-COLUMN TABLE}

@@

\subsection{MATHEMATICAL EXPRESSIONS}

All papers typeset by Copernicus Publications follow the math
typesetting regulations given by the IUPAC Green Book (IUPAC:
Quantities, Units and Symbols in Physical Chemistry, 2nd Edn., Blackwell
Science, available at:
http://old.iupac.org/publications/books/gbook/green\_book\_2ed.pdf,
1993).

@@

Multiplication signs are typeset using the LaTeX commands
\texttt{\textbackslash{}times} (for vector products, grids, and
exponential notations) or \texttt{\textbackslash{}cdot}

@@

\subsection{ALGORITHM}

If you want to use algorithms, you can either enable the required
packages in the header (the default, see \texttt{algorithms:\ true}), or
make sure yourself that the \LaTeX packages \texttt{algorithms} and
\texttt{algorithmicx} are installed so that \texttt{algorithm.sty}
respectively \texttt{algorithmic.sty} can be loaded by the Copernicus
template. Copernicus staff will remove all undesirable packages from
your LaTeX source code, so please stick to using the header option,
which only adds the two acceptable packages.

@@

\conclusions

The conclusion goes here. You can modify the section name with
\texttt{\textbackslash{}conclusions{[}modified\ heading\ if\ necessary{]}}.

\codedataavailability{use this to add a statement when having data sets and software code
available} %% use this section when having data sets and software code available

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Figures and tables in appendices}

Regarding figures and tables in appendices, the following two options
are possible depending on your general handling of figures and tables in
the manuscript environment: \subsection{Option 1} If you sorted all
figures and tables into the sections of the text, please also sort the
appendix figures and appendix tables into the respective appendix
sections. They will be correctly named automatically.
\subsection{Option 2} If you put all figures after the reference list,
please insert appendix tables and figures after the normal tables and
figures.

To rename them correctly to A1, A2, etc., please add the following
commands in front of them: \texttt{\textbackslash{}appendixfigures}
needs to be added in front of appendix figures
\texttt{\textbackslash{}appendixtables} needs to be added in front of
appendix tables

Please add \texttt{\textbackslash{}clearpage} between each table and/or
figure. Further guidelines on figures and tables can be found below.
\noappendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontribution{Karstens wrote code and paper build on work of Bodirsky. Bodirsky and
Popp revised paper.} %% optional section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\competinginterests{The authors declare no competing interests.} %% this section is mandatory even if you declare that no competing interests are present

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\disclaimer{We like Copernicus.} %% optional section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
Thanks to the rticles contributors!
\end{acknowledgements}

%% REFERENCES
%% DN: pre-configured to BibTeX for rticles

%% The reference list is compiled as follows:
%%
%% \begin{thebibliography}{}
%%
%% \bibitem[AUTHOR(YEAR)]{LABEL1}
%% REFERENCE 1
%%
%% \bibitem[AUTHOR(YEAR)]{LABEL2}
%% REFERENCE 2
%%
%% \end{thebibliography}

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
\bibliographystyle{copernicus}
\bibliography{SOCbudget.bib}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

%% LITERATURE CITATIONS
%%
%% command                        & example result
%% \citet{jones90}|               & Jones et al. (1990)
%% \citep{jones90}|               & (Jones et al., 1990)
%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
%% \citeauthor{jones90}|          & Jones et al.
%% \citeyear{jones90}|            & 1990

\end{document}

>>>>

# Examples from the official template

## FIGURES

@@

## FIGURES

@@

### ONE-COLUMN FIGURES

Include a 12cm width figure of Nikolaus Copernicus from [Wikipedia](https://en.wikipedia.org/wiki/File:Nikolaus_Kopernikus.jpg) with caption using R Markdown.

### TWO-COLUMN FIGURES

@@

## TABLES

@@

### ONE-COLUMN TABLE

@@

### TWO-COLUMN TABLE

@@

## MATHEMATICAL EXPRESSIONS

All papers typeset by Copernicus Publications follow the math typesetting regulations given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry, 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).

@@

Multiplication signs are typeset using the LaTeX commands `\times` (for vector products, grids, and exponential notations) or `\cdot`

@@

## ALGORITHM

  If you want to use algorithms, you can either enable the required packages in the header (the default, see `algorithms: true`), or make sure yourself that the \LaTeX packages `algorithms` and `algorithmicx` are installed so that `algorithm.sty` respectively `algorithmic.sty` can be loaded by the Copernicus template.
Copernicus staff will remove all undesirable packages from your LaTeX source code, so please stick to using the header option, which only adds the two acceptable packages.

@@
